### 2023-08-28 README.Rmd

This repository contains the code and data necessary to reproduce the main results of the preprint ["Sentinel lead pipe racks quantify orthophosphate’s dose-response in drinking water"](https://doi.org/10.26434/chemrxiv-2023-h1459).

>>>>

This repository contains the code and data necessary to reproduce the main results of the preprint ["Evaluating sentinel pipe racks for monitoring lead release and optimizing corrosion control"](https://doi.org/10.26434/chemrxiv-2023-h1459).
